Fast Algorithms for Intersection of Nonmatching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex
WIP on benchmarks.

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
using \plucker coordinates, red values \notePE{***}. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 1D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

\subsection{General algorithms}

\begin{center}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}}
        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch}} & \colorbox{orange}{BBsearch} & \colorbox{Goldenrod}{BIHonly} \\ \hline
        BIH(AABB) & AABB & BIH(AABB) \\
        AFront & AFront & ---
    \end{tabular}
\end{center}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.43\textwidth]{\figpath test1_cube0.pdf}
    \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.}
    \label{fig:cube_mesh}
\end{figure}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
    \caption{}
    \label{fig:cube_speed}
\end{figure}

>>>>

We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
using \plucker coordinates, red values \notePE{***}. The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D. Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.

\subsection{General algorithms}
So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
intersection and advancing front method (shortly AFront) to prolong the intersection. From now on, we shall refer to an algorithm made of these components \emph{BIHsearch}. In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}). \emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows the AFront. The version 
\emph{BIHonly} computes AABB together with BIH, but does not use AFront.

\begin{table}[!htb]
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}
                    >{\centering\arraybackslash}p{20ex}}
        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch\vphantom{By}}} & \colorbox{orange}{BBsearch\vphantom{By}} & \colorbox{Goldenrod}{BIHonly\vphantom{By}} \\ \hline
        BIH(AABB) & AABB & BIH(AABB) \\
        AFront & AFront & ---
    \end{tabular}
    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.}
    \label{tab:search_algorithms}
\end{table}

Let us now start with the problem on an artificial mesh.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.43\textwidth]{\figpath test1_cube0.pdf}
    \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.
             The planes are also nonmatching, therefore can be seen as two independent components.}
    \label{fig:cube_mesh}
\end{figure}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
    \caption{asdf}
    \label{fig:cube_speed}
\end{figure}

Next, we study the performance of the intersection algorithms on a mesh of a real problem, see \fig{fig:bedrichov_meshes}. The mesh represents a mountain ridge in the Jizera mountains which 
includes a system of geological fractures (\fig{fig:bedrichov_cut}). We also used this model to create
a less real mesh, in which the fractures extend through the bulk surface (\fig{fig:bedrichov_extend}). 
However, this situation might rather occur in another application than porous media problem.

@@
